---
title: "LMwithPred"
author: "Marium K."
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
This is the Linear Model with Prediction problem. Predict strength scores using data from the following website.    

$H_0$: There is no difference in the given models and none of them is better than the other.  
$H_A$:There is a difference in the given models and one of them is better than the other.

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)  
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot)
```

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New,interval="prediction")
```


```{r}
plot(SIMS~GRIP,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
predict.lm(model.2,New,interval="prediction")
```

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=dataF)
summary.lm(model.3)
predict.lm(model.3,New,interval="prediction")
```

```{r}
anova(model.1,model.3)
```
As seen above, the p value is less than 1 which makes us reject the null hypothesis and conclude that there is a difference between the models and one of them is better than the other two. We concluded that based on the adjusted R-squared which was higher for model 1 than the other two models. 